\phantomsection
\subsection*{Libri e Articoli}
\addcontentsline{toc}{subsection}{Libri e Articoli}
\begin{itemize}

\item
Ferguson, A. G. (2017). The rise of big data policing: Surveillance, race, and the future of law enforcement.
\item
Floridi, L. (2005). The ontological interpretation of informational privacy. Ethics and Information Technology 7:185–200.
\item
Floridi, L. (2012). Big data and their epistemological challenge. Philosophy and Technology, 24(4), 435–437.
\item
Fuchs, C. (2010). StudiVZ: social networking in the surveillance society. Ethics Inf Technol 12:171–185.
\item
Heymann, D. L., \& Rodier, G. R. (2004). SARS: a global response to an international threat. Journal of World Affairs, 10(2), 185–197.
\item
Loi, M. \& Christen, M. (2019). Two Concepts of Group Privacy. Philosophy \& Technology.
\item
McCulloch, J., \& Wilson, D (2016). Pre-crime: Pre-emption, precaution and the future.
\item
Mittelstadt, B. (2017). From Individual to Group Privacy in Big Data Analytics. Philos. Technol. 30:475–494.
\item
Moor, J. H. (2001). The future of computer ethics: You ain’t seen nothin’ yet!. Ethics and Information Technology 3: 89–91.
\item
Moor, J. H. (2005). Why we need better ethics for emerging technologies. Ethics and Information Technology (2005) 7:111–119.
\item
Moor, J. H. (1985). What is Computer Ethics. Metaphilosophy 16(4):266 – 275.
\item
Stuart Ward, J. and Barker, A. (2013). Undefined by data: A survey of big data definitions. arXiv:1309.5821v1.
\item
Turilli, M. \& Floridi, L. (2009). The ethics of information transparency. Ethics Inf Technol 11:105–112.
\item
Wallace, K. A. (1999). Anonymity. Ethics and Information Technology 1: 23–35.
\item
Winter, J. S. (2014). Surveillance in ubiquitous network societies: normative conflicts related to the consumer in-store supermarket experience in the context of the Internet of Things. Ethics Inf Technol 16:27–41.

\end{itemize}

\phantomsection
\subsection*{Siti web}
\addcontentsline{toc}{subsection}{Siti web}
\begin{itemize}

\item
www.agi.it
\item
www.focus.it
\item
www.springer.com

\end{itemize}